Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-21 paper/paper.tex
Complete paper with all suggestions

\begin{figure}[ht]
  \begin{center}
  \includegraphics[scale=0.23]{images/attachments.png}
  \end{center}
  \caption{\label{attachments}Attachments analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/steps_to_reproduce.png}
  \end{center}
  \caption{\label{steps}Steps to reproduce analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/stack_traces.png}
  \end{center}
  \caption{\label{stack_traces}Stack traces analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/comment_complexity.png}
  \end{center}
  \caption{\label{comments}Comments complexity analysis.}
\end{figure}

@@

We concatenated all comments into a single large string in order to be analysed for total number of words. This step 
was performed at the end of each ticket's lifecycle. We ran our comments analysis on 201,786 tickets among which 
113,344 had comments and 88,442 did not have any comments.

@@

From the figure we cannot clearly deduce whether increased number of words in comments influence 
the Time-To-Close positively or negatively. However, a correlational analysis releaved a weak 
positive relationship with $r = 0.271$ and $p < 0.01$. This implies a statistically significant finding - 
as the number of comments increases, the time-to-close value of the ticket also increases.

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/fields_complexity.png}
  \end{center}
  \caption{\label{fields}Time-To-Close versus summary and description word count.}
\end{figure}

@@

The Figure shows a very similar correlation to the one for comments complexity. A correlational analysis revealed 
a weak positive relationship with $r = 0.178$ and $p < 0.01$. This implies both that our results are statistically 
significant and also that as number of words in summary and description increase, the Time-To-Close increases, thus 
the quality of the ticket decreases.

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/grammar_correctness.png}
  \end{center}
  \caption{\label{grammar}Grammar correctness score analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/sentiment_analysis.png}
  \end{center}
  \caption{\label{sentiment}Sentiment score analysis.}
\end{figure}

>>>>

\begin{figure}[ht]
  \begin{center}
  \includegraphics[scale=0.25]{images/attachments.png}
  \end{center}
  \caption{\label{attachments}Attachments analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
  \end{center}
  \caption{\label{steps}Steps to reproduce analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/stack_traces.png}
  \end{center}
  \caption{\label{stack_traces}Stack traces analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/comment_complexity.png}
  \end{center}
  \caption{\label{comments}Comments complexity analysis.}
\end{figure}

@@

We concatenated all comments into a single large string in order to be analysed for total number of words. This step 
was performed at the end of each ticket's lifecycle. We ran our comments analysis on 201,786 tickets among which 
113,344 had comments and 88,442 did not have any comments. What we calculated as being total number of words inside comments 
is all the words inside all comments corresponding to a ticket summed up.

@@

From the figure we cannot clearly deduce whether increased number of words in comments influence 
the Time-To-Close positively or negatively. Actually, we can assume at first sight that there is a descending trend implying more 
words produce smaller Time-To-Close values. However, the bulk of values plotted are in the range of 
1 to 1,600 total comment words per ticket (76,633 tickets) and in this slice of tickets, the trend is descending.
We did not generate the plot containing only these values because there would still be 36,711 tickets left out.

A correlational analysis ran on all 201,786 tickets, however, releaved a weak positive relationship with $r = 0.271$ and $p < 0.01$. 
This implies a statistically significant finding - as the number of comments increases, the time-to-close value of the ticket also increases.

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/fields_complexity.png}
  \end{center}
  \caption{\label{fields}Time-To-Close versus summary and description word count.}
\end{figure}

@@

The Figure shows a very similar correlation to the one for comments complexity - it seems that as the number of words 
in summary and description increases, the Time-To-Close will decrease. This is true for the majority of the tickets 
which are in the range of 2 to 290 words, but as in the case of comments complexity analysis, we did not generate 
the plot only for those as we would have left 61,322 tickets out (out of a total of 201,786 tickets analysed).

However, a correlational analysis ran on all 201,786 tickets revealed a weak positive relationship with $r = 0.178$ and $p < 0.01$. 
This implies both that our results are statistically significant and also that as number of words in summary and description increase, 
the Time-To-Close increases, thus the quality of the ticket decreases.

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/grammar_correctness.png}
  \end{center}
  \caption{\label{grammar}Grammar correctness score analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/sentiment_analysis.png}
  \end{center}
  \caption{\label{sentiment}Sentiment score analysis.}
\end{figure}
